\documentclass[letterpaper,11pt,usenames,dvipsnames]{article}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.3in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-1pt}\scshape\raggedright\small
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Pranchal Sharma}} & \textbf{Email :} \href{mailto:pranchalwork@gmail.com}{pranchalwork@gmail.com}\\
   \href{https://www.linkedin.com/in/pranchalsharma/}{https://www.linkedin.com/in/pranchalsharma/}
 & \textbf{Mobile} : +91 8448809671 \\          
  \href{https://github.com/pranchalsharma-github}{https://github.com/pranchalsharma-github
  }  &
  \textbf{Location} : Noida, IN 
\end{tabular*}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ABES Engineering College}{Ghaziabad}
      {Computer Science Engineering;  CGPA: \textbf{7.32}}{July 2019 -- Present}
      
      \resumeSubheading
      {Modern School}{Noida}
      {PCM;  CGPA: \textbf{7.92}}{April 2017 -- April 2018}
      
      \resumeSubheading
      {Modern School}{Noida}
      {CGPA: \textbf{10}}{April 2015 -- April 2016}
      
 
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
\resumeSubheading
      {Coregenic Softwares}{Noida}
      {Web Development Intern}{January 2022 -- March 2022}
      \resumeItemListStart
      
          \item{Developed user interfaces with modern JavaScript frameworks, HTML5 and CSS3.} 
          \item{Troubleshot and debugged code ensuring compatibility with devices, browsers and operating systems.}
          \item{Collaborated with project managers and development team to brainstorm new ideas.}
      \resumeItemListEnd
        \resumeSubheading
      {Dakhni}{Remote}
      {Freelance Visual Designer}{October 2020 -- August 2021}
      \resumeItemListStart
        \item{Created user-centered designs with integrated marketing information, creative assets and design patterns.}
        \item{Conceptualized and developed 20+ graphics products for Art and Literature projects using Adobe Illustrator and Adobe Photoshop.}
        \item{Adapted graphics for use in print and web platforms.}\\
      \resumeItemListEnd
   

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    
     \resumeItem{DevCode || React.js, Node.js, Socket.io || \MYhref{https://dev-code-editor.herokuapp.com/}{Github/Server Link} }

           A \textbf{real-time online code editor}
           where users can share an interactive editor and write code together.\\This application is based on the concept of operational transformation which forms the basis for a shared editor.

  \resumeSubHeadingListEnd
 
 \section{Achievements}
 \resumeSubHeadingListStart
 \resumeSubItem{CodeKaze 2022}
      {Secured 3298th rank all over India and scored 128/128.
      }
       \resumeSubItem{Sports}
      {Achieved 1 Silver and 3 Bronze medal (Roller Skating) at various State-Level
      Competitions.}
 \resumeSubHeadingListEnd
 
 \section{Position of Responsibilities}
 \resumeSubHeadingListStart
 \resumeSubItem{Graphics Coordinator at GeeksforGeeks ABESEC Chapter}
      {Created 20+ digital displays in total for the organization's social media presence and weekly technical events.
      }
          
\resumeSubItem{Graphic Design Volunteer at GirlUp Maitri, Orissa}
      {Designed visual content for social media which,\\in total, received over 25K points of engagement.}
 \resumeSubHeadingListEnd
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Expert}{: C, C++}
   }
        \textbf{\\Intermediate}{: Python, SQL, HTML, CSS, JavaScript, BootStrap, Git/Github}
         \textbf{\\Beginner}{: MongoDB, ReactJS, Java}
         \textbf{\\Soft Skills}{: Solution design, Multitasking, Collaboration, Oral communication skills}
   
 \resumeSubHeadingListEnd

%-------------------------------------------

%--------CERTIFICATES------------
\section{CERTIFICATIONS}
 \resumeSubHeadingListStart
   \item{
     \textbf{HTML, CSS, JavaScript for
Web Developers}{, Coursera}
   }
        \textbf{\\PCAP: Programming Essentials In
Python}{, Cisco NetAcad}
         \textbf{\\JavaScript for Beginners}{, SkillUp}
   
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
